# Estimation of Ultimate

We use the paid and reported development methods to estimate ultimate claims. Our selected ultimate in column [3] is our actuarial best estimate of the expected ultimate:

```{r sel-ult, fig.cap = "Estimated and Selected Ultimates"}
est_ult_display <- est_ult %>%
  blank_row() %>%
  totals_row(cols = 2:4, label_col = 1)

col_names <- htmltools::withTags(table(
    class = 'display',
    thead(
      tr(
        th(rowspan = 2, "Policy Period"),
        th(colspan = 3, "Estimated Ultimates")
      ),
      tr(
        th(
          "[1]",
          br(),
          "Paid Dev Method",
          style = 'text-align: center'
        ),
        th(
          "[2]",
          br(),
          "Reported Dev Method",
          style = 'text-align: center'
        ),
        th(
          "[3]",
          br(),
          "Selected",
          style = 'text-align: center'
        )
      )
    )
  ))

DT::datatable(
  est_ult_display,
  rownames = FALSE,
  container = col_names,
  options = list(
    dom = 't',
    ordering = FALSE,
    columnDefs = list(
      list(targets = 0, class = "dt-center")
    )
  ),
  escape = FALSE
) %>%
  formatCurrency(
    2:4,
    currency = "",
    digits = 0
  ) %>%
  frameWidget(height = '100%')
  
```

Notes:  
&nbsp;&nbsp;[1] *see figure \@ref(fig:paid-projection)*  
&nbsp;&nbsp;[2] *see figure \@ref(fig:rpt-projection)*  
&nbsp;&nbsp;[3] *selected based on actuarial judgement and results of ultimate estimation methods shown in columns [1] and [2]*

## Paid Development

The following table shows the paid development projections:

```{r paid-projection, fig.cap = "Paid Development Method"}
paid_proj_diplay <- paid_proj %>%
  blank_row() %>%
  totals_row(cols = c(3, 5), label_col = 1)


DT::datatable(
  paid_proj_diplay,
  rownames = FALSE,
  colnames = c("Policy Year", "Age", "[1] <br/> Paid", "[2] <br /> CDF", "[3] <br /> Estimated Ultimate"),
  options = list(
    dom = 't',
    ordering = FALSE,
    columnDefs = list(
      list(targets = 0:1, class = "dt-center")
    )
  ),
  escape = FALSE
) %>%
  formatCurrency(
    c(3, 5),
    currency = "",
    digits = 0
  ) %>%
  formatRound(
    4,
    digits = 3
  ) %>%
  frameWidget(height = '100%')
  
```

Notes:  
&nbsp;&nbsp;[1] *provided by `r params$company_short`*  
&nbsp;&nbsp;[2] *see figure \@ref(fig:paid-ata)*  
&nbsp;&nbsp;[3] *= [1] x [2]*  

To estimate the `CDF`s in column [2] we look at `r params$company_short`'s historical cumulative paid development as seen in figure \@ref(fig:paid-triangle) and loss development factors as shown in \@ref(fig:paid-ata).  Chanegs in the payment pattern can cause the paid development method to be inaccurate.

## Reported Development

```{r rpt-projection, fig.cap = "Reported Development Method"}
rpt_proj_diplay <- rpt_proj %>%
  blank_row() %>%
  totals_row(cols = c(3, 5), label_col = 1)


DT::datatable(
  rpt_proj_diplay,
  rownames = FALSE,
  colnames = c("Policy Year", "Age", "[1] <br/> Reported", "[2] <br /> CDF", "[3] <br /> Estimated Ultimate"),
  options = list(
    dom = 't',
    ordering = FALSE,
    columnDefs = list(
      list(targets = 0:1, class = "dt-center")
    )
  ),
  escape = FALSE
) %>%
  formatCurrency(
    c(3, 5),
    currency = "",
    digits = 0
  ) %>%
  formatRound(
    4,
    digits = 3
  ) %>%
  frameWidget(height = '100%')
  
```

Notes:  
&nbsp;&nbsp;[1] *provided by `r params$company_short`*  
&nbsp;&nbsp;[2] *see figure \@ref(fig:rpt-ata)*  
&nbsp;&nbsp;[3] *= [1] x [2]*  

To estimate the `CDF`s in column [2] we look at `r params$company_short`'s historical cumulative reported development as seen in figure \ref(fig:rpt-triangle) and loss development factors as shown in \ref(fig:rpt-ata).  Changes in case reserve adequacy can cause the reported development method to be inaccurate.
